Determinism, Complexity, and Predictability in Computer Performance

### 2014-02-04 pecomplexity.tex
Adding Joshua/Liz's initial comments on results

@@

>>>>

First paragraph: WPE is a good measure of predictability.  Figure:
best athlete MASE vs. its WPE.

@@

The structure being picked up on by WPE may be linear or nonlinear. When you have a low WPE and a high ARIMA it could be that the structure WPE is picking up is simply nonlinear structure that LMA can handle but ARIMA cannot. So while the ARIMA prediction look realy bad there is plenty of structure present as suggested by WPE and taken advantage of by LMA but since it is nonlinear ARIMA can't take it into account and does bad.

Second paragraph: full results.  Image: MASE vs. WPE for both LMA \&
ARIMA.  Points to make: (1) clusters are distributed differently (2)
clusters are shaped differently---tight or not (3) clusters move
differently between LMA and ARIMA (4) finally, the diagonal line is
important.  If you're below it, you could do better.
